The ordertrans() function

### 2021-01-17 inst/ordertrans.Rmd
slight clarification

In the above, object `x` is a named vector with elements
`seq_along(x)` in some order.  Technically `x` is an order vector
because it answers the question "where did the first-named competitor
come?"  (see also the discussion at `rrank.Rd`).  However, it might
equally be a rank vector because it answers the question "who came
first? who came second?".

@@

```{r,showordervec}
ordervec2supp(x)
ordervec2supp(o)
```

@@

```{r}
ordervec2supp(x) == ordervec2supp(o)
```

>>>>

In the above, object `x` is a named vector with elements
`seq_along(x)` in some order.  It means that competitor `d` came
second, competitor `a` came third, `b` came first and `c` came fourth.
Technically `x` is an order vector because it answers the question
"where did a particular competitor come?"  However, it might equally
be a rank vector because it answers the question "who came first? who
came second?"  (see also the discussion at `rrank.Rd`).

@@

```{r,showordervec}
(Sx <- ordervec2supp(x))
(So <- ordervec2supp(o))
```

@@

```{r}
Sx==So
```
